Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-02-01 Draft/shower.tex
small changes in shower.tex

is a bit mitigated if NLO+PS tools are used (compare LO+PS and NLO+PS from {\sc MG5\_aMC} with the fixed-NLO prediciton), however even at NLO+PS the central region 

@@

In conclusion, the comparison of tools including matching with parton-shower clearly shows the benefits of the inclusion of NLO corrections: for most observables described
effectively at NLO accuracy differences between tools are at (or below) the 10\% level. {\bf MZ compare this number with scale uncertainties} 
Some exceptions exist, e.g. the rapidity separation of the two tagging jets, which
on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make it still worth to investigate more in details the way QCD radiation is 
generated {\bf MZ cite here H VBF at NNLO?}. Finally, the size of discrepancies for observables that are described at a lower perturbative accuracy, notably those related to the third jet, suggest that 
experimental analyses should rely as least as possible on those observables and, in any case, use conservative estimate of the theory uncertainties. In order to improve the
description of these observables, a simulation of VBS+j at NLO, currently unavailable but within the reach of modern automated tools, is certainly desirable.

>>>>

is a bit mitigated if NLO+PS tools are used (compare LO+PS and NLO+PS from {\sc MG5\_aMC+Pythia8} with the fixed-NLO prediciton), however even at NLO+PS the central region 

@@

In conclusion, the comparison of tools including matching with parton-shower clearly shows the benefits of the inclusion of NLO corrections: for most observables described
effectively at NLO accuracy differences between tools are at (or below) the 10\% level. {\bf MZ compare this number with scale uncertainties} 
Some exceptions exist, e.g. the rapidity separation of the two tagging jets, which
on the one hand clearly suggest not to rely on a single tool/parton shower, and on the other make it worth to investigate more in details the way QCD radiation is 
generated {\bf MZ cite here H VBF at NNLO?}. Finally, the size of discrepancies for observables that are described at a lower perturbative accuracy, notably those related to the third jet, suggest that 
experimental analyses should rely as least as possible on those observables and, in any case, use conservative estimate of the theory uncertainties. In order to improve the
description of these observables, a simulation of VBS+j at NLO, currently unavailable but within the reach of modern automated tools, is certainly desirable.
